Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-05-13 ms.tex
minor clean up, specify statistical error on 857 GHz offset

\section{Data}
\label{sec:data}
All \PLANCK~data products utilized throughout this work are drawn from the 
\PLANCK~2013 release \citep{planck2013}. Specifically, we have made use 
of all six of the zodiacal light corrected HFI intensity maps
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}. Our 
full-resolution (6.1$'$ FWHM) SED fits neglect the two lowest HFI frequencies, 
100 and 143 GHz, as these have FWHM of 9.66$'$ and 7.27$'$ respectively.

@@

The following subsections detail the processing steps we have applied to 
isolate thermal emission from Galactic dust in the \PLANCK~maps and prepare
these maps for our joint \IRAS/\PLANCK~SED fits.

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible upon visual inspection 
in \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
are prominent from 100 to 353 GHz relative to the Galactic emission
we wish to characterize, especially at high latitudes. To remove the CMB 
anisotropies, we have subtracted the Spectral Matching Independent Component 
Analysis \citep[SMICA,][]{smica} model from each of the \PLANCK~maps, 
after applying appropriate unit conversions for the 545 and 857 GHz maps 
with native units of MJy/sr. Low-order corrections, particularly removal of the
residual Solar dipole, are discussed in $\S$\ref{sec:zp}.

@@

Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ in \PLANCK~band 
$\nu_i$ due to the CO transition from J=$N$ to J=$(N$$-$1). $I_3$ represents 
the Type 3 CO amplitude in  K$_{RJ}$ km/s of J=1$\rightarrow$0 emission. The 
$F_{12CO, \nu_i, N, N-1}$ are conversion factors between K$_{RJ}$ km/s and 
$K_{CMB}$ for particular band/transition pairs. The relevant values, 
calculated with the \textit{Unit Conversion and Colour Correction} software 
utilities (\verb|v1.2|), are:

@@

Specifically, we perform a linear fit to the FDS99-predicted 857 GHz values as 
a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
\PLANCK~857 GHz map with zodiacal light and point sources removed and smoothed 
to 1$^{\circ}$ FWHM, which we will refer to as $\mathcal{I}_{857}$. We 
consider $\mathcal{I}_{857}$ to be the independent variable, as it has much 
higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not a monochromatic 
prediction, as we have incorporated the finite bandpass correction factors 
described in $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine
the dust spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels 
with $\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to 
degree resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.

The formal statistical errors on these parameters are small. Just as in the 
case of performing the regression versus  H\,\textsc{i}, systematic problems 
dominate the uncertainty in the derived zero point offset. The systematics
likely to dominate our FDS-based zero level are imperfect zodiacal light 
corrections and the FDS99 temperature map. To quantify the level of systematic 
error, we split the sky into four quadrants, with the dividing boundaries being
$b$=0$^{\circ}$ and $l$=0$^{\circ}$, $l$=180$^{\circ}$. We again restricted to
$\mathcal{I}_{857}$$<$2.15 MJy/sr, and repeated the regression in each 
quadrant. The slopes varied from 0.948 to 0.993, with an rms of 0.0188, while 
the offsets varied from $-$0.056 MJy/sr to $+$0.089 MJy/sr, with an rms of 
0.0586 MJy/sr.

@@

% actually evaluate the statistical errors !!!!

>>>>

\section{Data}
\label{sec:data}
All \PLANCK~data products utilized throughout this work are drawn from the 
\PLANCK~2013 release \citep{planck2013}. Specifically, we have made use 
of all six of the zodiacal light corrected HFI intensity maps
\citep[\texttt{R1.10\_nominal\_ZodiCorrected},][]{planckzodi}. Our 
full-resolution (6.1$'$ FWHM) SED fits neglect the two lowest HFI frequencies, 
100 and 143 GHz, as these have FWHM of 9.66$'$ and 7.27$'$ respectively.
% in last sentence, reference Table 1 ?

@@

The following subsections detail the processing steps we have applied to 
isolate Galactic dust emission in the \PLANCK~maps in preparation for our joint
\PLANCK/\IRAS~SED fits. % reference fitting section at end of this sentence ?

\subsection{CMB Anisotropy Removal}
\label{sec:cmb}
We first addressed the CMB anisotropies before performing any of the 
interpolation/smoothing described in $\S$\ref{sec:ptsrc}/$\S$\ref{sec:smth}. 
The CMB anisotropies are effectively imperceptible upon visual inspection 
in \PLANCK~857 GHz, but can be perceived at a low level in \PLANCK~545 GHz, and
are prominent at 100-353 GHz relative to the Galactic emission
we wish to characterize, especially at high latitudes. To remove the CMB 
anisotropies, we have subtracted the Spectral Matching Independent Component 
Analysis \citep[SMICA,][]{smica} model from each of the \PLANCK~maps, 
after applying appropriate unit conversions for the 545 and 857 GHz maps 
with native units of MJy/sr. Low-order corrections, particularly removal of the
residual Solar dipole, are discussed in $\S$\ref{sec:zp}.

@@

Where $I_{CO, \nu_i, N, N-1}$ is the intensity in $K_{CMB}$ in \PLANCK~band 
$\nu_i$ due to the CO transition from J=$N$ to J=$(N$$-$1). $I_3$ represents 
the appropriately smoothed Type 3 CO amplitude in  K$_{RJ}$ km/s of 
J=1$\rightarrow$0 emission. The $F_{12CO, \nu_i, N, N-1}$ are conversion 
factors between K$_{RJ}$ km/s and $K_{CMB}$ for particular band/transition 
pairs. The relevant values, calculated with the \textit{Unit Conversion and 
Colour Correction} software utilities (\verb|v1.2|), are:

@@

Specifically, we perform a linear fit to the FDS99-predicted 857 GHz values as 
a function of \PLANCK~857 GHz. For this purpose, we employ a version of the 
\PLANCK~857 GHz map with zodiacal light and point sources removed and smoothed 
to 1$^{\circ}$ FWHM, which we will refer to as $\mathcal{I}_{857}$. We 
consider $\mathcal{I}_{857}$ to be the independent variable, as it has much 
higher S/N than the FDS99 prediction, henceforward referred to as 
$\mathcal{F}_{857}$. Note that $\mathcal{F}_{857}$ is not simply the FDS99
model evaluated at 857 GHz, but also incorporates the color correction factor 
of $\S$\ref{sec:bpcorr}, using the FDS99 temperature map to determine the dust 
spectrum shape. We then rebin to $N_{side}$=64 and restrict to pixels with 
$\mathcal{I}_{857}$$<$2.15 MJy/sr. Since \PLANCK~857 GHz smoothed to degree 
resolution has very high S/N, we can safely perform such a cut on 
$\mathcal{I}_{857}$. Figure \ref{fig:fdsref} shows a scatterplot of 
$\mathcal{I}_{857}$ versus $\mathcal{F}_{857}$, with a moving median and linear
fit overplotted. The linear fit was performed with uniform weights and 
iterative outlier rejection. The best-fit linear model is given by 
$\mathcal{F}_{857}$=0.994$\mathcal{I}_{857}$$-$0.018. It is encouraging that 
the slope is quite close to unity, and the offset near zero.

% i evaluated the `formal statistical error' using the covar keyword in
% hogg_iter_linfit

The formal statistical error on the best-fit 857 GHz offset is quite small, 
$\sim$0.002 MJy/sr. The systematics likely to dominate the actual uncertainty 
on our FDS-based zero level are imperfections in the \PLANCK/\verb|i100| 
zodiacal light models and the FDS99 temperature map. To quantify these 
systematic uncertainties, we split the sky into four quadrants, with the 
dividing boundaries being $b$=0$^{\circ}$ and $l$=0$^{\circ}$, 
$l$=180$^{\circ}$. We again restricted to $\mathcal{I}_{857}$$<$2.15 MJy/sr, 
and repeated the regression in each quadrant. The slopes varied from 0.948 to 
0.993, with an rms of 0.0188, while the offsets varied from $-$0.056 MJy/sr to
$+$0.089 MJy/sr, with an rms of 0.0586 MJy/sr.

% in previous sentence, think it might be better to only quote rms, and
% omit the ranges of values for each parameter ?

@@
